---
title: "SDS315_HW3"
author: "Aaron Coronado, acc5483"
date: "2024-01-30"
output:
  html_document:
    toc: yes
    toc_float: yes
    df_print: paged
  pdf_document: default
---

```{r Setup, message = F, warning = F, echo = F}
library(tidyverse)
library(mosaic)
library(kableExtra)
creatinine <- read_csv("creatinine.csv")
marketmodel <- read_csv("marketmodel.csv")
covid <- read_csv("covid.csv")
milk <- read_csv("milk.csv")
```

# **Homework 3**

## **Problem 1**

### **(A)**

Using the functions *lm()* and *coef()*, I was able to determine the intercept and slope of the fitted model are 147.81 and -0.62, respectively. After plugging those into the linear regression equation I was left with the following:

$\hat{y}$ = 147.81 - 0.62x.

When I substituted 55 for x, I calculated a creatinine clearance rate of 113.71 mL/minute.

### **(B)**

The rate of creatinine clearance decreases by approximately -0.62 mL/minute per year. I determined this by simply interpreting the slope, which I had previously determine in Part A.

### **(C)**

Using the linear regression equation from Part A, I determined that the predicted creatinine clearance rate for the 40yro and the 60yro was 123.01 mL/min and 110.61 mL/min, respectively. Then I subtracted the actual rate from the predict rate and was left with a difference of 11.99 mL/min for the 40yro and a difference of 1.39 mL/min for the 60yro. As the difference for the 40yro was greater than that of 60yro, the 40yro has the healthier creatinine clearance rate.

## **Problem 2**

```{r Problem 2, message = F, waring = F, echo = F}
appl_mod = lm(AAPL ~ SPY, data = marketmodel)
goog_mod = lm(GOOG ~ SPY, data = marketmodel)
mrk_mod = lm(MRK ~ SPY, data = marketmodel)
jnj_mod = lm(JNJ ~ SPY, data = marketmodel)
wmt_mod = lm(WMT ~ SPY, data = marketmodel)
tgt_mod = lm(TGT ~ SPY, data = marketmodel)

stocks <- tibble(Ticker_Symbol = c("AAPL", "GOOG", "MRK", "JNJ", "WMT", "TGT"),
                 Intercept = c(coef(appl_mod)[1], coef(goog_mod)[1], coef(mrk_mod)[1], coef(jnj_mod)[1], coef(wmt_mod)[1], coef(tgt_mod)[1]),
                 Slope = c(coef(appl_mod)[2], coef(goog_mod)[2], coef(mrk_mod)[2], coef(jnj_mod)[2], coef(wmt_mod)[2], coef(tgt_mod)[2]),
                 R_Squared = c(rsquared(appl_mod), rsquared(goog_mod), rsquared(mrk_mod), rsquared(jnj_mod), rsquared(wmt_mod), rsquared(tgt_mod)))

kable_styling(kbl(stocks))
```

The figure above displays a table of six individual stocks as well as their respective alphas, betas, and coefficient of determinations. A stock's beta is essentially a measure of that stock's volatility compared to the market. A beta of 1 indicates the stocks moves relatively insync with the market. A beta of greater than 1 indicates a greater volatility in comparison with the market, and a beta of less than 1 indicates the opposite. All in all, beta helps investers assess the risks and returns of stocks and helps in making informed decisions while investing.
Apple stock has the highest systematic risk as it has the highest beta, and WMT has the least systematic risk as it has the lowest beta.

## **Problem 3**

```{r Problem 3, message = F, waring = F, echo = F}
ggplot(covid) +
  geom_line(aes(x = days_since_first_death, y = deaths, color = country)) +
  labs(x = "Days Since First Death", y = "Deaths")
```

Italy's estimated growth rate is 0.183 with a doubling time of 4 days.

Spain's estimated growth rate is 0.276 with a doubling time of 3 days.

## **Problem 4**

```{r Problem 4 Log Graph, message = F, warning = F, echo = F}
ggplot(milk) +
  geom_point(aes(x = log(price), y = log(sales)))
```

```{r Problem 4 Calculations, message = F, warning = F, echo = F, eval = F}
lm_milk = lm(log(sales) ~ log(price), data = milk)
coef(lm_milk)
```

When milk prices change by 1%, we expect milk sales to change by -1.62%. I came to this conclusion by running a regression on log(price) and log(sales) and then calling the coefficients of the regression.